### 2024-06-20 conteudo/tool/functionalities.tex
do not know what is, done in 19/06

	\begin{item}
		\textbf{Pattern Filter:} This filter make the explorer ignore every pair of duplicated functions that does not match a pattern
		given by the user as a parameter. We say that a function matches a pattern if the string formed by the concatenation of
		the relative path of the code file plus the function name. The user can define if both functions or at least one of the 
		functions in the pair need to match the pattern by given a specific parameter.
	\end{item}
\end{itemize}

>>>>

	\begin{item}
		\textbf{Pattern filter:} This filter make the explorer ignore every pair of duplicated functions that does not match a pattern
		given by the user as a parameter. We say that a function matches a pattern if the string formed by the concatenation of
		the relative path of the code file plus the function name. The user can define if both functions or at least one of the 
		functions in the pair need to match the pattern by given a specific parameter.
	\end{item}
\end{itemize}
